---
title: "Advanced Bioinformatics 2021 assessment"
author: "Martin Bird m1703202"
date: "12/04/2021"
output: html_document
---

# Task 3.1
```{r}
sum(5:55)
```

Sum(x:y) adds all integers from x to y

# Task 3.2
```{r}
sumfun <- function(n)
sum (5:n)
```

Like the previous task but allows us to change the input parameter
```{r}
sumfun (10)
sumfun (20)
sumfun (100)
```

# Task 3.3

I needed a variable to increment with every loop (++) but I didn't know how to that. I know that the fibonnaci sequence is Fn = Fn-1 + Fn-2 but only for n > 2 for this sequence.

Therefore I set the first two terms to be one and once the counting variable counts up (n) I can print fibonnaci past 1, 1,
```{r}
x <- 12
fib <- numeric(x)
fib[1] <- 1
fib[2] <- 1
for (x in 3:12) {
  fib[x] <- fib[x-1]+fib[x-2] 
}
print(fib)
```


# Task 3.4

```{r}
library(ggplot2)
ggplot(data=mtcars,aes(x=as.factor(gear),y=mpg)) + geom_boxplot(aes(col=as.factor(gear)))
```

Gears are the x axis.
Mpg is the y axis.
Boxes coloured accoring to gear

# Task 3.5

```{r}
y <- cars$dist; x <- cars$speed;
model <- lm(formula="y~x")
model
summary(model)
```

Answers to question:
Fitted slope: 3.932, Std. Error: 0.4155
Intercept: -17.579, Std. Error: 6.7584
Speed is in miles per hour (mph), dist is in feet (ft), found that out using ?cars

# Task 3.6

```{r}
library(ggplot2)
ggplot(cars,aes(speed,dist)) + geom_point() +
  geom_smooth(method="lm",formula="y~x")
```

# Task 3.7

I'm quite bad at maths and I don't know what to do here. My best guess of a place to start is to convert the units from mph to ft/s

```{r}
y <- cars$dist; x <- 1.467*cars$speed;
model <- lm(formula="y~x")
model
```






